Kaggle Competition: Restaurant Revenue Prediction
========================================================
Author: Rami Al-Fahham

### Exploratory Analysis

##### Import data
```{r}
train <- read.csv("train.csv", stringsAsFactors=FALSE, sep=",", dec = ".")
test <- read.csv("test.csv", stringsAsFactors=FALSE, sep=",", dec = ".")
```

##### Quick overview of data structure and descriptive statistics
```{r message=FALSE, warning=FALSE}
require(ggplot2)
require(lattice)

#Quick summary
str(train)
str(test)
summary(train)
```


train$sample <- 1
test$revenue <- 0
test$sample <- 0

total <- rbind(train, test)


##### Data preparation
```{r}
setup_predictors <- function(df){

  df$year   <- as.numeric(substr(df$Open.Date, 7, 10))

  df$month  <- as.numeric(substr(df$Open.Date, 1, 2))

  df$day  <- as.numeric(substr(df$Open.Date, 4, 5))
  
  df
}

total <- setup_predictors(total)

# Drop City, City.Group, Type
# (a) due to missing values
# (b) Relevant predictors: P1, P2-P37 representing demographic, real estate and commercial data for each restaurant
train <- subset(total[-c(2,3,4,5)], sample == 1)
test <- subset(total[-c(2,3,4,5)], sample == 0)
```


### Tree-based Methods
  + Random Forest
```{r message=FALSE, warning=FALSE}
require(randomForest)
require(MASS)
```

##### Fit Random Forest Model
```{r eval=FALSE}
# Model for bike casual demand

# Find optimal number of randomly selected variables for a given number of trees
set.seed(5)
tuneRF(train[-c(1,39,40)], train$revenue, mtryStart = 7, ntreeTry = 10000, stepFactor = 2, improve = 0.001)

# Random forest model
set.seed(71)
rf.rev <- randomForest(revenue ~ ., data = train[,-1], ntree=10000, mtry = 4, importance = TRUE)
```


#### Predict revenue and write file to submit
```{r eval=FALSE}
rfPred <- round(predict(rf.rev, test[,-1]))

# Build dataframe with results
rfSubmit <- data.frame(Id = test$Id, Prediction = rfPred)

# Write results to .csv for submission
write.csv(rfSubmit, file = "randomForestPred.csv", row.names=FALSE)
```
### Score using Random Forest (250000 trees, mtry = 4): 1718594.02449
